---
title: "The Price of a Big Mac Through Time & Space"
author: "pdwarf"
date: "11/10/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Big Mac Index Data

The following graphic uses data published by The Economist on github which is the 
basis for the famously known *Big Mac Index*:  https://github.com/TheEconomist/big-mac-data

My graph will show the price (in USD) of a Big Mac in 7 countries or areas around the world, from 2001 to 2018:

- USA
- China
- Russia
- Great Britain
- India
- Euro Zone
- Norway (because here, the Big Mac was always most expensive, until recently)

## Slide with R Output

```{r, echo = TRUE, message=FALSE, eval=FALSE}
library(tidyverse)
library(plotly)

URL <-
    "https://raw.githubusercontent.com/TheEconomist/big-mac-data/master/output-data/big-mac-full-index.csv"

BigMacIndex <- 
    read_csv(URL)

BigMacIndex %>%
    filter(iso_a3 %in% 
               c("NOR", "GBR", "CHN", "RUS",
                 "USA", "EUZ", "IND")) %>%
    plot_ly(x = ~date) %>%
    add_lines(y = ~dollar_price, 
              color = ~ factor(iso_a3))
```

## Slide with Plot

```{r, echo = FALSE, message=FALSE, eval=TRUE}
library(tidyverse)
library(plotly)

BigMacIndex <- 
    read_csv("https://raw.githubusercontent.com/TheEconomist/big-mac-data/master/output-data/big-mac-full-index.csv")

BigMacIndex %>%
    filter(iso_a3 %in% c("NOR", "GBR", "CHN", "RUS",
                         "USA", "EUZ", "IND")) %>%
    plot_ly(x = ~date) %>%
    add_lines(y = ~dollar_price, color = ~ factor(iso_a3))
```

